Binning Strategies and Related Loss for Large Data

### 2015-03-02 Paper.Rnw
More apt subsection title
Minor caption and label edits

\subsection{Extensions to Rectangular Binning}

@@

\begin{figure}[H]
  \centering
  \subfloat[Standard Binning]{\includegraphics[keepaspectratio=true, width=3in]{./figure/Binning-DataAndBin.pdf}}
%   \subfloat{\includegraphics[keepaspectratio=TRUE, width=2in]
%   {./figure/RandomBinningDataPoints1}}
  \subfloat[Random Binning]{\includegraphics[keepaspectratio=TRUE, width=3in]
  {./figure/RandomBinningDataPoints2.pdf}}
  \caption{Visualization of how data pairs are assigned to bins centered at (5, 25) and (15,25) under the two rectangular binning algorithms. Points in the standard algorithm are contained within the defined bin region, where points from the random algorithm may be assigned to bins from outside the defined bin regions.}
  \label{fig:BinningTutorial}
\end{figure}

@@

\subsection{Quantile Binning Algorithm}

>>>>

\subsection{Extension to Two Dimensional Binning}

@@

\begin{figure}[H]
  \centering
  \subfloat[Standard Binning]{\includegraphics[keepaspectratio=true, width=3in]{./figure/Binning-DataAndBin.pdf}}
%   \subfloat{\includegraphics[keepaspectratio=TRUE, width=2in]
%   {./figure/RandomBinningDataPoints1}}
  \subfloat[Random Binning]{\includegraphics[keepaspectratio=TRUE, width=3in]
  {./figure/RandomBinningDataPoints2.pdf}}
  \caption{Visualization of how data pairs are assigned to bins centered at (5, 25) and (15,25) under the two rectangular binning algorithms. Points in the standard algorithm are contained within the defined bin region, where points from the random algorithm may be assigned to any of the surrounding bin centers.}
  \label{fig:BinningTutorial}
\end{figure}

@@

\subsection{Quantile Binning Algorithm (old - to be removed)}
